```{r}
#| include: false
source("_common.R")
d <- site_data(site_id)
s <- d$site
t <- d$target
h <- d$harvest
gmaps <- sprintf("https://www.google.com/maps/search/?api=1&query=%.6f,%.6f", s$lat, s$lon)
```

::: {.column-screen}
```{=html}
<iframe src="../maps/`r site_id`.html" title="Interactive parcel map" style="width:100%; height:78vh; border:0; display:block;" loading="lazy"></iframe>
```
:::

[Open the map full screen](../maps/`r site_id`.html){target="_blank"} · Click a parcel for its statistics. Switch the background imagery (Esri, Google, Bing, OSM) and toggle layers in the top-right panel.

## Summary

```{r}
#| results: asis
cat(sprintf(
  "The house point (%.6f, %.6f) is in **%s** and falls on cadastral **sheet %s, parcel %s**, a %s m² parcel (cadastral record: %s m²). ",
  s$lat, s$lon, h$comune %||% "the comune", t$Foglio, t$particella, num(t$area_m2),
  ifelse(is.na(t$area_cadastral_m2) | t$area_cadastral_m2 == 0, "not recorded", num(t$area_cadastral_m2))
))
cat(sprintf(
  "The ground lies between %s and %s m above sea level (mean %s m). The mean slope is %s° (%s%%, %s), and the parcel faces %s on average. %s%% of its area faces SE–SW. ",
  num(t$elev_min), num(t$elev_max), num(t$elev_mean), num(t$slope_mean, 1), num(t$slope_mean_pct),
  slope_word(t$slope_mean), ifelse(is.na(t$aspect_dir), "no particular direction (flat)", t$aspect_dir),
  num(t$south_facing_pct)
))
cat(ifelse(
  is.na(t$buildings_n) | t$buildings_n == 0,
  "No cadastral building lies on the parcel.",
  sprintf("The cadastral map shows %s building(s) on the parcel (%s), %s m² in total.",
          t$buildings_n, t$buildings, num(t$buildings_m2))
), "\n")
```

- **Coordinates:** [`r sprintf("%.6f, %.6f", s$lat, s$lon)`](`r gmaps`){target="_blank"} (Google Maps)
- **Cadastre portal:** [`r h$comune %||% s$cadastre_portal`](`r s$cadastre_portal`){target="_blank"}
- **Parcels within `r s$buffer_m` m:** `r nrow(d$stats)`

## Terrain

```{r}
tibble(
  Measure = c("Elevation (m)", "Slope (°)", "Mean slope (%)", "Mean aspect",
              "South-facing area (SE–SW)", "Southness (−1 north … +1 south)",
              "Noon sun, winter solstice (× flat ground)", "Noon sun, equinox (× flat ground)"),
  Value = c(
    sprintf("min %s · mean %s · max %s", num(t$elev_min, 1), num(t$elev_mean, 1), num(t$elev_max, 1)),
    sprintf("min %s · mean %s · max %s", num(t$slope_min, 1), num(t$slope_mean, 1), num(t$slope_max, 1)),
    num(t$slope_mean_pct),
    ifelse(is.na(t$aspect_mean_deg), "flat", sprintf("%s° (%s)", num(t$aspect_mean_deg), t$aspect_dir)),
    paste0(num(t$south_facing_pct), "%"),
    num(t$southness, 2),
    num(t$sun_winter_idx, 2),
    num(t$sun_equinox_idx, 2)
  )
) |> knitr::kable()
```

The statistics come from the Regione Piemonte 5 m LiDAR terrain model (2009–2011). Slope and aspect are computed on the 5 m grid and resampled to 1 m, so that small parcels are measured over their own footprint. The model shows bare ground and misses buildings, trees and any earthworks since 2011.

## Planning and constraints

```{r}
#| results: asis
o <- d$overlays
if (nrow(o) == 0) {
  cat("No planning or landscape layer from the comune's GIS intersects this parcel.\n")
} else {
  for (i in seq_len(nrow(o))) {
    v <- as.character(t[[o$col[i]]])
    cat(sprintf("- **%s** (%s): %s  \n  %s\n",
                o$en[i], o$layer[i],
                ifelse(is.na(v) | v == "", "*does not apply to this parcel*", v),
                o$description[i]))
  }
}
```

::: {.callout-warning}
These layers come from the comune's public GIS viewer and are for orientation only. Check the current town plan (PRG) and the certificato di destinazione urbanistica with the comune before relying on them.
:::

## Cadastral record

```{r}
raw <- c("parcel_id", "Foglio", "particella", "area_cadastral_m2", "Perimeter", "Sezione",
         "DataIn", "DataFi", "Irr", "ConStr", "FID", "Gislink")
orig <- c(parcel_id = "Parcel ID", Foglio = "Foglio", particella = "Acad_text",
          area_cadastral_m2 = "Area", Perimeter = "Perimeter", Sezione = "Sezione",
          DataIn = "DataIn", DataFi = "DataFi", Irr = "Irr", ConStr = "ConStr",
          FID = "FID", Gislink = "Gislink")
raw <- intersect(raw, names(t))
tibble(
  Field = vapply(orig[raw], tr_field, ""),
  `Original field` = unname(orig[raw]),
  Value = vapply(raw, \(f) { v <- trimws(as.character(t[[f]])); ifelse(is.na(v) | v == "", "(blank)", v) }, "")
) |> knitr::kable()
```

## Surrounding parcels

All parcels touching the `r s$buffer_m` m buffer around the point, nearest first.

```{r}
#| column: page
d$stats |>
  transmute(
    Parcel = paste0(parcel_id, ifelse(is_target %in% c(TRUE, "TRUE"), " ★", "")),
    `Distance (m)` = num(dist_to_point_m),
    `Area (m²)` = num(area_m2),
    `Elev. mean (m)` = num(elev_mean),
    `Slope mean (°)` = num(slope_mean, 1),
    Aspect = ifelse(is.na(aspect_dir), "flat", aspect_dir),
    `South-facing` = paste0(num(south_facing_pct), "%"),
    `Winter sun` = num(sun_winter_idx, 2),
    Buildings = ifelse(is.na(buildings_n) | buildings_n == 0, "", as.character(buildings_n))
  ) |>
  knitr::kable(align = "lrrrrlrrr")
```

## Data and method

- **Cadastre:** `r h$comune %||% ""` GisMaster portal, ArcGIS REST service at `r h$arcgis_rest_root`. Harvested `r substr(h$harvested_at, 1, 10)`. Parcels are stored exactly as served. Other layers are cropped to the study area.
- **Terrain:** Regione Piemonte, *Ripresa aerea ICE 2009–2011 – DTM 5 m* (CC BY 4.0), from the regional WCS service.
- **Harvested data and code:** [data/`r site_id`](https://github.com/EBukin/house-search/tree/main/data/`r site_id`) and [R/](https://github.com/EBukin/house-search/tree/main/R) in the repository.
